Comparison of MCMC algorithms in Stochastic Volatility Models

### 2023-09-27 manuscript/main.tex
updated plots

\usepackage[natbibapa]{apacite}
\bibliographystyle{apacite}
% \usepackage[longnamesfirst,authoryear, round]{natbib}
% \bibliographystyle{unsrtnat}

\usepackage[
top    = 1.0in,
bottom = 1.2in,
left   = 1.0in,
right  = 1.0in]{geometry}
\linespread{1.5}

@@

    \subsection{Centered paramterisation}

    \subsubsection{Hamiltonian Monte Carlo}

    \subsubsection{Gaussian Mixture Approximation}

    \subsection{Reparameterised models}

    \subsubsection{Hamiltonian Monte Carlo}

    \subsubsection{Gaussian Mixture Approximation}

@@

>>>>

\usepackage[natbibapa]{apacite}
\bibliographystyle{apacite}
% \usepackage[longnamesfirst,authoryear, round]{natbib}
% \bibliographystyle{unsrtnat}
\usepackage{float}
\usepackage[
top    = 1.0in,
bottom = 1.2in,
left   = 1.0in,
right  = 1.0in]{geometry}
\linespread{1.5}

@@

    \subsection{Hamiltonian Monte Carlo}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_1k.png}
        \caption{Distribution of rank statistics for centered and non centered Hamiltoninan Monte Carlo (static parameters). Non centered histograms look approximately uniform. The centered parameterisation struggles to estimate $\sigma^2$}
    \end{figure}

    \subsection{Gaussian Mixture Approximation}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/ksc_1k.png}
        \caption{Distribution of rank statistics for centered and non centered Gaussian mixture model(static parameters). All parameters display a lack of calibration}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_1k.png}
        \caption{Distribution of rank statistics for weighted resampled model (static parameters) with 1000 SBC iterations. All parameters display a lack of calibration}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_5k.png}
        \caption{Distribution of rank statistics for weighted resampled model (static parameters) with 5000 SBC iterations. Increasing number of SBC parameters does not improve results}
    \end{figure}

    \subsection{All models and parameters}
    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/dist_chisq.png}
        \caption{Distribution of chi squared statistics for all models.}
    \end{figure}
